The \raveon\ catalog of stellar atmospheric parameters and\\ chemical abundances for chemo-dynamic studies in the \gaia\ era

### 2016-09-09 article/unrave.tex
Updated abstract, final paragraphs, etc

%% This file is part of the unRAVE Project 
%% Copyright 2016 the authors.  All rights reserved.

@@

\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\thecannon}{\project{The~Cannon}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\galah}{\project{\acronym{GALAH}}}
\newcommand{\ges}{\project{Gaia-ESO}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\aspcap}{\project{\acronym{ASPCAP}}}
\newcommand{\lamost}{\project{\acronym{LAMOST}}}
\newcommand{\hipparcos}{\project{Hipparcos}}
\newcommand{\epic}{\project{K2/EPIC}}
\newcommand{\sdss}{\project{\acronym{SDSS}}}
\newcommand{\tgas}{\project{\acronym{TGAS}}}
\newcommand{\unrave}{\project{unRAVE}}

@@

% TODO: Final checks based on released version.
\newcommand{\Nstarsqc}{447,207} % v0.95 finite values
\newcommand{\Nabundances}{1,692,825} %v0.95 finite values

@@

\begin{document}
\title{The \project{unRAVE} catalog of stellar atmospheric parameters and\\
chemical abundances for chemo-dynamic studies in the \gaia\ era}

\author{
Andrew R. Casey\altaffilmark{1}, 
Keith Hawkins\altaffilmark{1}, 
David W. Hogg\altaffilmark{2,3,4,5}, 
Melissa Ness\altaffilmark{5}, 
Hans Walter-Rix\altaffilmark{5}, 
Georges Kordopatis\altaffilmark{6}, 
Andrea Kunder\altaffilmark{6}, 
Matthias Steinmetz\altaffilmark{6}, 
Sergey Koposov\altaffilmark{1}, 
Harry Enke\altaffilmark{6}, 
Jason Sanders\altaffilmark{1}, 
Gerry Gilmore\altaffilmark{1}, 
Toma\v{z} Zwitter\altaffilmark{6}, 
Kenneth C. Freeman\altaffilmark{7}, 
Luca Casagrande\altaffilmark{7}, 
Gal~Matijevi\v{c}\altaffilmark{6}, 
George Seabroke\altaffilmark{8}, 
Olivier Bienayme\altaffilmark{9}, 
Joss Bland-Hawthorn\altaffilmark{10}, 
Brad~K.~Gibson\altaffilmark{11}, 
Eva~K.~Grebel\altaffilmark{12}, 
Amina Helmi\altaffilmark{13}, 
Ulisse Munari\altaffilmark{14}, 
Julio F. Navarro\altaffilmark{15,16}, 
Warren Reid\altaffilmark{17,18}, 
Arnaud Siebert\altaffilmark{19},
Rosemary Wyse\altaffilmark{20}\\
\vspace{2em}
\emph{(Affiliations can be found at the end of the article)}
}

\begin{abstract}
The Milky Way is a powerful laboratory for understanding galaxy formation,
as it can provide orbits, ages, atmospheric parameters, as well as chemical 
abundances for vast sets of individual stars.  These inferences require 
both astrometric and spectroscopic data.  Indeed, in order to be maximally
useful for chemo-dynamic studies, the Tycho-Gaia Astrometric Solution 
(\tgas) sample in the first \gaia\ data release requires a spectroscopic 
complement that includes radial velocities, stellar atmospheric parameters, and 
elemental abundances.  Among existing spectroscopic samples, the RAdial 
Velocity Experiment (\rave) survey has the largest overlap with \tgas: 
over 200,000 stars.  We present a data-driven re-analysis of \rave\ 
spectra using \thecannon, and we provide more precise and accurate stellar
parameters and abundances than available in previous \rave\ data releases. 
We constructed our model using high-fidelity \apogee\ stellar parameters 
and abundances for red giant branch stars that overlap with \rave, and 
stellar parameters from the \project{K2}/\project{Ecliptic Pole Input 
Catalog} for main-sequence and sub-giant branch stars.  We derive, and 
validate, improved effective temperature $\teff$, surface gravity $\logg$, 
and chemical abundances of up to seven elements (O, Mg, Al, Si, Ca, Fe, Ni) 
for \Nstarsqc\ stars.  In total we report \Nabundances\ elemental 
abundances, with a typical precision of 0.07~dex.  The \unrave\ catalog 
presented here, in conjunction with \tgas, represents the most powerful 
data set for chemo-dynamic analysis at the dawn of broadly available 
\gaia\ data.
\end{abstract}

@@

The first \gaia\ data release will include the Tycho-Gaia Astrometric Solution
\citep[hereafter \tgas;][]{Michalik_2015a,Michalik_2015b}: positions, proper 
motions, and parallaxes for approximately two million stars in the Tycho-2 
\citep{Hog_2000} catalog.  After cross-matching all major stellar spectroscopic 
surveys\footnote{Specifically we cross-matched the Tycho-2 catalog against the 
\apogee\ DR13 \citep{Zasowski_2013}, \ges\ internal DR4 
\citep{Gilmore_2012,Randich_2013}, \galah\ internal DR1 \citep{DeSilva_2015}, 
\lamost\ DR1 \citep{Cui_2012}, and \rave\ DR4 \citep{Steinmetz_2006} catalogs.}, 
we found that the RAdial Velocity Experiment \citep[\rave;][]{Steinmetz_2006} 
survey is expected to have the largest overlap with the first \gaia\ 
% TODO: Sanders: 292,036; Kunder: 264,276
data release: up to 264,276 stars.  We used the \gaia\ universe model snapshot 
\citep{Robin_2012} to estimate the precision in parallax and proper motions that
could be available in the first \gaia\ data release (DR1) for stars in those 
overlap samples.  Comparing the expected precision to what is currently available, 
we further found that the \rave\ survey will benefit most from \gaia\ DR1: the
distances of 63\% of stars in the \rave--\gaia\ DR1 overlap sample are expected 
to improve with the first \gaia\ data release, and 47\% of stars are likely to
have better proper motions.  Although the \gaia\ universe model assumes 
end-of-mission uncertainties --- and does not account for systematics in the 
first data release --- this calculation still provides intuition for the relative
improvement that the first \gaia\ data release can make to ground-based surveys.  
The expected improvements for \rave\ motivated us to examine what chemical 
abundances were available from those data, and to evaluate whether we could 
enable new chemo-dynamic studies by contributing to the existing set of chemical
abundances.

@@

In Figure \ref{fig:gold-standard-hrd} we show Hertzsprung-Russell diagrams 
for the \rave\ stars that overlap with these studies.  We only include stars 
with $\chi_r^2 < 3$ and $S/N > 10$~pixel$^{-1}$, although the latter cut 
removed only a few stars because the average S/N in the \rave\ spectra for
these stars is relatively high ($\gtrsim{}50$~pixel$^{-1}$).  The literature 
data points in Figure \ref{fig:gold-standard-hrd} are linked to our derived
labels for the same stars, illustrating good qualitative agreement across 
the turn-off and sub-giant branch in all studies.  If we treat all three 
studies as a single point of comparison, the bias between our work and these 
studies is $-89$~K in $\teff$, just $-0.06$~dex in $\logg$, and $-0.03$~dex 
in [Fe/H] (see Figure~\ref{fig:gold-standard-comparison}).  The RMS deviation
in labels is 237~K, 0.30~dex, and 0.15~dex, respectively.  When considering 
the relative information content available in \rave\ (945~pixels in the near 
infrared with $\mathcal{R} \approx 7{,}500$) compared to these literature 
studies that use \project{Hipparcos} parallaxes where possible, and base 
their inferences on spectra with resolving power $\mathcal{R}$ between 
40,000 to 110,000, and S/N ratios exceeding 150, we consider the agreement 
to be very satisfactory.  Indeed, given the metallicity precision available
in the \unrave\ catalog, these results will likely be useful for future 
studies based on exoplanet host star properties (e.g., 
\project{TESS}\footnote{At present, however, there are just $\approx$30 
stars in \rave\ that overlap with the compilations of exoplanet host star 
properties listed at \texttt{exoplanets.org} and \texttt{exoplanets.eu}.}).

@@

There are 142 stars that overlap between \rave\ and the fourth internal
data release of the \ges\ survey. These are a mix of main-sequence, 
sub-giant and red giant branch stars.  About half (67) of the sample 
were acquired with the \acronym{UVES} instrument --- the other with the 
\acronym{GIRAFFE} spectrograph --- and the S/N of the \ges\ spectra peaks 
at $\approx140$~pixel$^{-1}$.  Despite most of these stars having relatively 
low S/N ratios in \rave\ ($\approx 25$~pixel$^{-1}$), there is good agreement
in with \ges\ and the \unrave\ stellar parameters (Figure~\ref{fig:ges-stellar-parameters}).  
The RMS in effective temperature, surface gravity and metallicity is 233~K, 
0.37~dex, and 0.17~dex, respectively.

@@

We have presented a comprehensive collection of precise stellar abundances 
for stars in the first \gaia\ data release.  In total we derive reliable 
stellar atmospheric parameters for \Nstarsqc, and report more than 1.69 
million abundances.  Despite the caveats and limitations discussed here, 
our validation experiments and comparisons with high-resolution 
spectroscopic studies suggests that our results have sufficient accuracy 
and precision to be useful for chemo-dynamic studies that become imminently 
feasible only in the era of \gaia\ data.  Indeed, we are optimistic that 
the \unrave\ catalog will advance understanding of the Milky Way's 
formation and evolution.

@@

% TODO: Replace ZENODO-URL with a data url
\noindent{}Source code for this project is available at \texttt{\giturl}\hspace{-0.5em},
and this document was compiled from revision hash \texttt{\githash} in that repository.
Inferred labels, associated errors, and relevant metadata are available electronically
at \texttt{\url{ZENODO-URL}} \citep{ZENODO-CITATION}.  These results are also available
through the \rave\ DR5 database \citep{Kunder_2016}. Please note that it is a condition
of using these results that the fifth \rave\ data release by \citet{Kunder_2016} must 
also be cited, as the work presented here would not have been possible without the 
tireless efforts of the entire \rave\ collaboration, past and present.

@@

\bibitem[Wojno et al.(2016)]{Wojno_2016} Wojno, J., et al.\ 2016, submitted

@@

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/gold-standard-hrd.pdf}
\caption{Hertsprung-Russell diagrams of stars in common between this work and that of \citet{Bensby_2014,Reddy_2003,Reddy_2006,Valenti_Fischer_2005}.  Stars are colored by the metallicity of each study. Circles indicate literature markers in the first three panels, and the linked triangles indicate \project{unRAVE} parameters for the same object. This figure illustrates the good qualitative agreement in the shape of the turnoff and sub-giant branch.\label{fig:gold-standard-hrd}}
\end{figure*}

@@

\begin{figure}[p]
\center
\includegraphics[width=0.65\textwidth]{figures/gce.pdf}
\caption{Detailed chemical abundances ([X/Fe]) for giant stars in \unrave\ with respect to [Fe/H], showing the Galactic chemical evolution derived for each element. Bin densities are scaled logarithmically. Note that the y-axis limits vary for each panel, however for clarity we show the scaled-solar position by dashed lines, and have common tick mark spacing on the y-axis for all panels. Only stars meeting our quality constraints are shown (see Section \ref{sec:discussion}).\label{fig:gce}}
\end{figure}

@@

\altaffiltext{1}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
\altaffiltext{2}{Simons Center for Data Analysis, 160 Fifth Avenue, 7th floor, New York, NY 10010, USA}
\altaffiltext{3}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY 10003, USA}
\altaffiltext{4}{Center for Data Science, New York University, 726 Broadway, 7th floor, New York, NY 10003, USA}
\altaffiltext{5}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{6}{University of Ljubljana, Faculty of Mathematics and Physics, Jadranska 19, 1000 Ljubljana, Slovenia}
\altaffiltext{7}{Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, ACT 2611, Australia}
\altaffiltext{8}{Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, RH5 6NT, UK}
\altaffiltext{9}{Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l?Universit\'e, F-67000 Strasbourg, France}
\altaffiltext{10}{Sydney Institute for Astronomy, School of Physics, University of Sydney, NSW 2006, Australia}
\altaffiltext{11}{E.A. Milne Centre for Astrophysics, University of Hull, Hull, HU6 7RX, United Kingdom}
\altaffiltext{12}{Astronomisches Rechen-Institut, Zentrum f\"ur Astronomie der Universit\"at Heidelberg, M\"onchhofstr.\ 12--14, 69120 Heidelberg, Germany}
\altaffiltext{13}{Kapteyn Astronomical Institute, University of Groningen, P.O. Box 800, 9700 AV Groningen, The Netherlands}
\altaffiltext{14}{INAF Astronomical Observatory of Padova, 36012 Asiago (VI), Italy}
\altaffiltext{15}{Department of Physics and Astronomy, University of Victoria, Victoria, BC, Canada V8P 5C2}
\altaffiltext{16}{Senior CIfAR Fellow}
\altaffiltext{17}{Department of Physics and Astronomy, Macquarie University, Sydney, NSW 2109, Australia}
\altaffiltext{18}{Western Sydney University, Penrith South DC, NSW 1797}
\altaffiltext{19}{Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l?Universit\'e, F-67000 Strasbourg, France}
\altaffiltext{20}{Johns Hopkins University, Baltimore, MD, USA}

>>>>

%% This file is part of the RAVE-on Project 
%% Copyright 2016 the authors.  All rights reserved.

@@

\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\thecannon}{\project{The~Cannon}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\galah}{\project{\acronym{GALAH}}}
\newcommand{\ges}{\project{Gaia-ESO}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\aspcap}{\project{\acronym{ASPCAP}}}
\newcommand{\lamost}{\project{\acronym{LAMOST}}}
\newcommand{\hipparcos}{\project{Hipparcos}}
\newcommand{\epic}{\project{K2/EPIC}}
\newcommand{\sdss}{\project{\acronym{SDSS}}}
\newcommand{\tgas}{\project{\acronym{TGAS}}}
\newcommand{\raveon}{\rave-on}

@@

\newcommand{\ReportedStellarParameters}{441,397} % catalog v0.97
\newcommand{\ReportedAbundances}{1,685,851} % catalog v0.97

@@

\begin{document}
\title{The \raveon\ catalog of stellar atmospheric parameters and\\
chemical abundances for chemo-dynamic studies in the \gaia\ era}

\author{
Andrew~R.~Casey\altaffilmark{1},
Keith~Hawkins\altaffilmark{1},
David~W.~Hogg\altaffilmark{2,3,4,5},
Melissa~Ness\altaffilmark{5},
Hans~Walter-Rix\altaffilmark{5},
Georges~Kordopatis\altaffilmark{6},
Andrea~Kunder\altaffilmark{6},
Matthias~Steinmetz\altaffilmark{6},
Sergey~Koposov\altaffilmark{1},
Harry~Enke\altaffilmark{6},
Jason~Sanders\altaffilmark{1},
Gerry~Gilmore\altaffilmark{1},
Toma\v{z}~Zwitter\altaffilmark{6},
Kenneth~C.~Freeman\altaffilmark{7},
Luca~Casagrande\altaffilmark{7},
Gal~Matijevi\v{c}\altaffilmark{6},
George~Seabroke\altaffilmark{8},
Olivier~Bienaym\'e\altaffilmark{9},
Joss~Bland-Hawthorn\altaffilmark{10},
Brad~K.~Gibson\altaffilmark{11},
Eva~K.~Grebel\altaffilmark{12},
Amina~Helmi\altaffilmark{13},
Ulisse~Munari\altaffilmark{14},
Julio~F.~Navarro\altaffilmark{15,16},
Warren~Reid\altaffilmark{17,18},
Arnaud~Siebert\altaffilmark{9},
Rosemary~Wyse\altaffilmark{19}\\
\vspace{2em}
\emph{(Affiliations can be found at the end of the article)}
}

\begin{abstract}
The orbits, atmospheric parameters, chemical abundances, and ages of 
individual stars in the Milky Way provide the most comprehensive 
illustration of galaxy formation available.  The Tycho-\gaia\ 
Astrometric Solution (\tgas) will deliver astrometric parameters for
the largest ever sample of Milky Way stars, though its full potential
cannot be realized without the addition of complementary spectroscopy.  
Among existing spectroscopic surveys, the RAdial Velocity Experiment 
(\rave) has the largest overlap with \tgas\ ($\gtrsim$200,000 stars).  
We present a data-driven re-analysis of \Nspectra\ \rave\ spectra using 
\thecannon.  For red giants, we build our model using high-fidelity 
\apogee\ stellar parameters and abundances for stars that overlap 
with \rave.  For main-sequence and sub-giant stars, our model uses 
stellar parameters from the \epic\ catalog.  We derive and validate 
effective temperature $\teff$, surface gravity $\logg$, and chemical 
abundances of up to seven elements (O, Mg, Al, Si, Ca, Fe, Ni).  We 
report a total of \ReportedAbundances\ elemental abundances with a 
typical precision of 0.07~dex, a substantial improvement over past 
\rave\ data releases.  The synthesis of \raveon\ and \tgas\ is the 
most powerful data set for chemo-dynamic analyses of the Milky Way ever produced.
\end{abstract}

@@

The first \gaia\ data release will include the Tycho-Gaia Astrometric Solution
\citep[hereafter \tgas;][]{Michalik_2015a,Michalik_2015b}: positions, proper 
motions, and parallaxes for approximately two million stars in the Tycho-2 
\citep{Hog_2000} catalog.  After cross-matching all major stellar spectroscopic 
surveys\footnote{Specifically we cross-matched the Tycho-2 catalog against the 
\apogee\ DR13 \citep{Zasowski_2013}, \ges\ internal DR4 
\citep{Gilmore_2012,Randich_2013}, \galah\ internal DR1 \citep{DeSilva_2015}, 
\lamost\ DR1 \citep{Cui_2012}, and \rave\ DR4 \citep{Steinmetz_2006} catalogs.}, 
we found that the RAdial Velocity Experiment \citep[\rave;][]{Steinmetz_2006} 
survey is expected to have the largest overlap with the first \gaia\ 
data release: up to 264,276 stars.  We used the \gaia\ universe model snapshot 
\citep{Robin_2012} to estimate the precision in parallax and proper motions that
could be available in the first \gaia\ data release (DR1) for stars in those 
overlap samples.  Comparing the expected precision to what is currently available, 
we further found that the \rave\ survey will benefit most from \gaia\ DR1: the
distances of 63\% of stars in the \rave--\gaia\ DR1 overlap sample are expected 
to improve with the first \gaia\ data release, and 47\% of stars are likely to
have better proper motions.  Although the \gaia\ universe model assumes 
end-of-mission uncertainties --- and does not account for systematics in the 
first data release --- this calculation still provides intuition for the relative
improvement that the first \gaia\ data release can make to ground-based surveys.  
The expected improvements for \rave\ motivated us to examine what chemical 
abundances were available from those data, and to evaluate whether we could 
enable new chemo-dynamic studies by contributing to the existing set of chemical
abundances.

@@

In Figure \ref{fig:gold-standard-hrd} we show Hertzsprung-Russell diagrams 
for the \rave\ stars that overlap with these studies.  We only include stars 
with $\chi_r^2 < 3$ and $S/N > 10$~pixel$^{-1}$, although the latter cut 
removed only a few stars because the average S/N in the \rave\ spectra for
these stars is relatively high ($\gtrsim{}50$~pixel$^{-1}$).  The literature 
data points in Figure \ref{fig:gold-standard-hrd} are linked to our derived
labels for the same stars, illustrating good qualitative agreement across 
the turn-off and sub-giant branch in all studies.  If we treat all three 
studies as a single point of comparison, the bias between our work and these 
studies is $-89$~K in $\teff$, just $-0.06$~dex in $\logg$, and $-0.03$~dex 
in [Fe/H] (see Figure~\ref{fig:gold-standard-comparison}).  The RMS deviation
in labels is 237~K, 0.30~dex, and 0.15~dex, respectively.  When considering 
the relative information content available in \rave\ (945~pixels in the near 
infrared with $\mathcal{R} \approx 7{,}500$) compared to these literature 
studies that use \project{Hipparcos} parallaxes where possible, and base 
their inferences on spectra with resolving power $\mathcal{R}$ between 
40,000 to 110,000, and S/N ratios exceeding 150, we consider the agreement 
to be very satisfactory.  Indeed, given the metallicity precision available
in the \raveon\ catalog, these results will likely be useful for future 
studies based on exoplanet host star properties (e.g., 
\project{TESS}\footnote{At present, however, there are just $\approx$30 
stars in \rave\ that overlap with the compilations of exoplanet host star 
properties listed at \texttt{exoplanets.org} and \texttt{exoplanets.eu}.}).

@@

There are 142 stars that overlap between \rave\ and the fourth internal
data release of the \ges\ survey. These are a mix of main-sequence, 
sub-giant and red giant branch stars.  About half (67) of the sample 
were acquired with the \acronym{UVES} instrument --- the other with the 
\acronym{GIRAFFE} spectrograph --- and the S/N of the \ges\ spectra peaks 
at $\approx140$~pixel$^{-1}$.  Despite most of these stars having relatively 
low S/N ratios in \rave\ ($\approx 25$~pixel$^{-1}$), there is good agreement
in with \ges\ and the \raveon\ stellar parameters (Figure~\ref{fig:ges-stellar-parameters}).  
The RMS in effective temperature, surface gravity and metallicity is 233~K, 
0.37~dex, and 0.17~dex, respectively.

@@

We have presented a comprehensive collection of precise stellar abundances 
for stars in the first \gaia\ data release.  In total we derive stellar 
atmospheric parameters for \ReportedStellarParameters\ stars, and report more 
than 1.69 million abundances.  Despite the caveats and limitations discussed here, 
our validation experiments and comparisons with high-resolution spectroscopic
studies suggests that our results have sufficient accuracy and precision to
be useful for chemo-dynamic studies that become imminently feasible only in
the era of \gaia\ data.  We are optimistic that the \raveon\ catalog will 
advance understanding of the Milky Way's formation and evolution.

@@

\noindent{}Source code for this project is available at \texttt{\giturl}\hspace{-0.5em},
and this document was compiled from revision hash \texttt{\githash} in that repository.
Derived labels, associated errors, and relevant metadata are available electronically
through the \rave\ from 19 September 2016 onwards. Please note that it is a condition
of using these results that the fifth \rave\ data release by \citet{Kunder_2016} must 
also be cited, as the work presented here would not have been possible without the 
tireless efforts of the entire \rave\ collaboration, past and present.

@@

\bibitem[Wojno et al.(2016)]{Wojno_2016} Wojno, J., et al.\ 2016, in preparation

@@

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/gold-standard-hrd.pdf}
\caption{Hertsprung-Russell diagrams of stars in common between this work and that of \citet{Bensby_2014,Reddy_2003,Reddy_2006,Valenti_Fischer_2005}.  Stars are colored by the metallicity of each study. Circles indicate literature markers in the first three panels, and the linked triangles indicate \raveon\ parameters for the same object. This figure illustrates the good qualitative agreement in the shape of the turnoff and sub-giant branch.\label{fig:gold-standard-hrd}}
\end{figure*}

@@

\begin{figure}[p]
\center
\includegraphics[width=0.65\textwidth]{figures/gce.pdf}
\caption{Detailed chemical abundances ([X/Fe]) for giant stars in \raveon\ with respect to [Fe/H], showing the Galactic chemical evolution derived for each element. Bin densities are scaled logarithmically. Note that the y-axis limits vary for each panel, however for clarity we show the scaled-solar position by dashed lines, and have common tick mark spacing on the y-axis for all panels. Only stars meeting our quality constraints are shown (see Section \ref{sec:discussion}).\label{fig:gce}}
\end{figure}

@@

% A magic, bad, hack.
\noindent{}$^{1}${Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK} \\
$^{2}${Simons Center for Data Analysis, 160 Fifth Avenue, 7th floor, New York, NY 10010, USA} \\
$^{3}${Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY 10003, USA} \\
$^{4}${Center for Data Science, New York University, 726 Broadway, 7th floor, New York, NY 10003, USA} \\
$^{5}${Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany} \\
$^{6}${University of Ljubljana, Faculty of Mathematics and Physics, Jadranska 19, 1000 Ljubljana, Slovenia} \\
$^{7}${Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, ACT 2611, Australia} \\
$^{8}${Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, RH5 6NT, UK} \\
$^{9}${Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l'Universit\'e, F-67000 Strasbourg, France} \\
$^{10}${Sydney Institute for Astronomy, School of Physics, University of Sydney, NSW 2006, Australia} \\
$^{11}${E.A. Milne Centre for Astrophysics, University of Hull, Hull, HU6 7RX, United Kingdom} \\
$^{12}${Astronomisches Rechen-Institut, Zentrum f\"ur Astronomie der Universit\"at Heidelberg, M\"onchhofstr.\ 12--14, 69120 Heidelberg, Germany} \\
$^{13}${Kapteyn Astronomical Institute, University of Groningen, P.O. Box 800, 9700 AV Groningen, The Netherlands} \\
$^{14}${INAF Astronomical Observatory of Padova, 36012 Asiago (VI), Italy} \\
$^{15}${Department of Physics and Astronomy, University of Victoria, Victoria, BC, Canada V8P 5C2} \\
$^{16}${Senior CIfAR Fellow} \\
$^{17}${Department of Physics and Astronomy, Macquarie University, Sydney, NSW 2109, Australia} \\
$^{18}${Western Sydney University, Penrith South DC, NSW 1797} \\
$^{19}${Johns Hopkins University, Baltimore, MD, USA} \\
